\begin{招待講演}{1}

\bibitem{04末石智大01}
末石智大:高速光学系制御に基づくダイナミックビジョンシステムとその応用,第3回産業ロボット関連技術の標準化学術研究会,2022.

\bibitem{ykuga36619767}
空閑洋平, mdx: データ活用社会創成プラットフォーム構築の現状と今後, CloudWeek 2021@Hokkaido University, 2 Sep, 2021.

\bibitem{ykuga36619729}
空閑洋平, NetTLP: ハードウェアと協調動作可能なソフトウェアPCIeデバイス開発環境, 情報処理学会 FIT 情報科学技術フォーラム トップコンファレンスセッション, 26 Aug, 2021.



%\bibitem{suzumura-mdx2022}
%Toyotaro Suzumura, Akiyoshi Sugiki, Hiroyuki Takizawa, Akira Imakura, Hiroshi Nakamura, Kenjiro Taura, Tomohiro Kudoh, Toshihiro Hanawa, Yuji Sekiya, Hiroki Kobayashi, Shin Matsushima, Yohei Kuga, Ryo Nakamura, Renhe Jiang, Junya Kawase, Masatoshi Hanai, Hiroshi Miyazaki, Tsutomu Ishizaki, Daisuke Shimotoku, Daisuke Miyamoto, Kento Aida, Atsuko Takefusa, Takashi Kurimoto, Koji Sasayama, Naoya Kitagawa, Ikki Fujiwara, Yusuke Tanimura, Takayuki Aoki, Toshio Endo, Satoshi Ohshima, Keiichiro Fukazawa, Susumu Date, Toshihiro Uchibayashi, "mdx: A Cloud Platform for Supporting Data Science and Cross-Disciplinary Research Collaborations", https://arxiv.org/abs/2203.14188

\bibitem{suzumura-nci2021}
鈴村豊太郎, “mdx: A platform for the data-driven future”、オーストラリア国立研究所NCI(National Computational Infrastructure)-Fujitsu HPC, Cloud and Data Futures Workshop, 2022年02月

\bibitem{suzumura-nanotec2021}
鈴村豊太郎, "データ活用社会創成プラットフォームmdxにおけるマテリアルズ・インフォマティクス研究・共創に向けて", 第20回ナノテクノロジー総合シンポジウム, 2022年01月

\bibitem{suzumura-canon2021}
鈴村豊太郎, "人工知能を支えるグラフニューラルネットワークの最新動向", 2021年度キャノングローバル戦略研究所主催「経済・社会との分野横断的研究会」, 2021年12月


\end{招待講演}

\begin{招待論文}{1}

\bibitem{02早川智彦01}
早川智彦,石川正俊,亀岡弘之:時速100km走行でのトンネル覆工コンクリート高解像度変状検出手法,建設機械施工,vol.73,no.8,pp.19-23,2021.

\bibitem{02早川智彦02}
早川智彦,望戸雄史,石川正俊,大西偉允,亀岡弘之:【大臣賞】時速100km走行での覆工コンクリート高解像度変状検出手法,土木施工,vol.62,no.7,p.146,2021.

\bibitem{04末石智大02}
Yuri Mikawa,Tomohiro Sueishi,Yoshihiro Watanabe,and Masatoshi Ishikawa:Dynamic Projection Mapping for Robust Sphere Posture Tracking Using Uniform / Biased Circumferential Markers,2022 IEEE Conference on Virtual Reality and 3D User Interfaces (VR2022),(TVCG Invited)2022.


\end{招待論文}

\begin{受賞}{1}

\bibitem{03黄守仁01}
村上健一,黄守仁,石川正俊,山川雄司:高速ビジュアルフィードバックを用いた高速３次元位置補償システムの開発,第22回計測自動制御学会システムインテグレーション部門講演会(SI2021),講演会論文集,pp.1403-1405,優秀講演賞,2021.

\bibitem{04末石智大03}
末石智大,石川正俊:手指高速トラッキングに向けた楕円群指輪マーカーの開発,第22回計測自動制御学会システムインテグレーション部門講演会(SI2021),講演会論文集,pp.1382-1387,優秀講演賞,2021.

\bibitem{kobayashi1-1}
小林博樹:情報通信技術の導入が困難なインフラ圏外空間を対象とした情報デザインとIoTの研究,ドコモ・モバイル・サイエンス賞　社会科学部門　優秀賞，2021/9．

\bibitem{kobayashi1-2}
Hill Hiroki Kobayashi, Radioactive Live Soundscape, Winner, Universal Design Expert, Institute for Universal Design KG, Germany, 2021/05．
\bibitem{JIANG3-1}
Renhe Jiang et al., "DL-Traff: Survey and Benchmark of Deep Learning Models for Urban Traffic Prediction", 30th ACM International Conference on Information and Knowledge Management (CIKM), Best Resource Paper Runner Up, 2021.

\end{受賞}

\begin{著書}{1}

\bibitem{05宮下令央01}
宮下令央:有名論文ナナメ読み「Shader Lamps: Animating Real Objects With Image-Based Illumination」,情報処理学会,情報処理,Vol.62,No.5 ,2021.


\end{著書}

\begin{雑誌論文}{1}

\bibitem{01石川正俊01}
川原大宙,妹尾拓,石井抱,平野正浩,岸則政,石川正俊：輪郭情報に基づくテンプレートマッチングを用いた重畳車両の高速トラッキング,計測自動制御学会論文集,58巻,1号,pp.21-30,2022.

\bibitem{01石川正俊02}
小山佳祐,堀邊隆介,安田博,万偉偉,原田研介,石川正俊：ワンボード・USB給電タイプの高速・高精度近接覚センサの開発とプリグラスプ制御の解析,日本ロボット学会誌,Vol.39,No.9,pp.862-865,2021.

\bibitem{01石川正俊03}
Masahiro Hirano,YujiYamakawa,Taku Senoo and Masatoshi Ishikawa：An acceleration method for correlation-based high-speed object tracking,Measurement Sensors,Vol.18,Article No.100258,2021.

\bibitem{01石川正俊04}
Masahiko Yasui,Yoshihiro Watanabe,and Masatoshi Ishikawa：Wide viewing angle with a downsized system in projection-type integral photography by using curved mirrors,Optics Express,Vol.29,Issue8,pp.12066-12080,2021.

\bibitem{01石川正俊05}
Ruimin Cao,Jian Fu,Hui Yang,Lihui Wang,and Masatoshi Ishikawa:Robust optical axis control of monocular active gazing based on pan-tilt mirrors for high dynamic targets,Optics Express,Vol.29,No.24,pp.40214-40230,2021.

\bibitem{02早川智彦03}
Kenichi Murakami,Tomohiko Hayakawa,and Masatoshi Ishikawa: Hybrid surface measuring system for motion-blur compensation and focus adjustment using a deformable mirror,Applied Optics,vol.61,Issue2,pp.429-438,2022.

\bibitem{02早川智彦04}
Yuki Kubota,Yushan Ke,Tomohiko Hayakawa,Yushi Moko,and Masatoshi Ishikawa：Optimal Material Search for Infrared Markers under Non-Heating and Heating Conditions,Sensors,Vol.21,Issue 19,Article No.6527,pp.1-17,2021.


\bibitem{04末石智大04}
Yuri Mikawa,Tomohiro Sueishi,Yoshihiro Watanabe,and Masatoshi Ishikawa:Dynamic Projection Mapping for Robust Sphere Posture Tracking Using Uniform/Biased Circumferential Markers,IEEE Transaction on Visualization and Computer Graphics,1-1,2021 (Early Access).

\bibitem{04末石智大05}
松本明弓,新田暢,末石智大,石川正俊:高速注視点推定を用いた広域高解像度投影システムの実現,計測自動制御学会論文集,Vol.58,No.1,pp.42-51,2022.

\bibitem{05宮下令央02}
井倉 幹大,宮下令央,山下 淳,石川 正俊,淺間 一:高速点滅LEDマーカと複数のRGB-Dセンサを用いた遮蔽領域を提示可能な任意視点重畳映像生成システム,精密工学会誌,Vol. 88,No.3,2022.

\bibitem{05宮下令央03}
Leo Miyashita,Akihiro Nakamura,Takuto Odagawa,and Masatoshi Ishikawa: BIFNOM Binary-Coded Features on Normal Maps,Sensors,Vol.21,No.10,Article No.3469,2021.


\bibitem{06田畑智志01}
Hongjin Xu,Lihui Wang,Satoshi Tabata,Yoshihiro Watanabe,and Masatoshi Ishikawa:Extended depth-of-field projection method using a high-speed projector with a synchronized oscillating variable-focus lens,Applied Optics,Vol.60,Issue 13,pp.3917-3924,2021.

\bibitem{08金賢梧01}
Hyuno Kim,and Masatoshi Ishikawa:Sub-Frame Evaluation of Frame Synchronization for Camera Network Using Linearly Oscillating Light Spot,Sensors,Vol.21,Issue 18,Article No.6148,pp.1-14,2021.

\bibitem{ykuga36595746}
Yukito Ueno, Ryo Nakamura, Yohei Kuga, Hiroshi Esaki, A NIC-driven Architecture for High-speed IP Packet Forwarding on General-purpose Servers, Journal of Information Processing, 30, pp226-237, 2022.

\bibitem{JIANG1-1}
Renhe Jiang, Zekun Cai, Zhaonan Wang, Chuang Yang, Zipei Fan, Quanjun Chen, Xuan Song, and Ryosuke Shibasaki, "Predicting Citywide Crowd Dynamics at Big Events: A Deep Learning System", ACM Trans. Intell. Syst. Technol. (TIST), 13, 2, Article 21, April 2022.
\bibitem{JIANG1-2}
Zipei Fan, Chuang Yang, Zhiwen Zhang, Xuan Song, Yinghao Liu, Renhe Jiang, Quanjun Chen, and Ryosuke Shibasaki, "Human Mobility-based Individual-level Epidemic Simulation Platform", ACM Trans. Spatial Algorithms Syst. (TSAS), 8, 3, Article 19, September 2022.
\bibitem{JIANG1-3}
Chuang Yang, Zhiwen Zhang, Zipei Fan, Renhe Jiang, Quanjun Chen, Xuan Song, Ryosuke Shibasaki, "EpiMob: Interactive Visual Analytics of Citywide Human Mobility Restrictions for Epidemic Control", IEEE Transactions on Visualization and Computer Graphics (TVCG), 2022.
\bibitem{JIANG1-4}
Renhe Jiang, Zekun Cai, Zhaonan Wang, Chuang Yang, Zipei Fan, Quanjun Chen, Kota Tsubouchi, Xuan Song, Ryosuke Shibasaki, "DeepCrowd: A Deep Model for Large-Scale Citywide Crowd Density and Flow Prediction", IEEE Transactions on Knowledge and Data Engineering (TKDE), 2021.
\bibitem{JIANG1-5}
Jinliang Deng, Xiusi Chen, Zipei Fan, Renhe Jiang, Xuan Song, and Ivor W. Tsang, "The Pulse of Urban Transport: Exploring the Co-evolving Pattern for Spatio-temporal Forecasting", ACM Trans. Knowl. Discov. Data (TKDD), 15, 6, Article 103, May 2021.
\bibitem{HNakamura1}
山下智也，宮本大輔，関谷勇司，中村宏, ``通信挙動に基づいたスキャン攻撃検
知'', 情報処理学会論文誌~デジタル社会の情報セキュリティとトラスト~特集
号，11pages, Vol.62，No.12，pp.67-83


\end{雑誌論文}

\begin{査読付}{1}


\bibitem{01石川正俊06}
Hiromichi Kawahara,Taku Senoo,Idaku Ishii,Masahiro Hirano,Norimasa Kishi and Masatoshi Ishikawa:High-speed tracking for overlapped vehicles using Instance Segmentation and contour deformation,2022 IEEE/SICE International Symposium on System Integration (SII2022),Proceedings,pp.730-735,2022.

\bibitem{01石川正俊07}
石川正俊：高速ビジョンを用いた高速知能ロボット,ロボット,No.263,pp.56-58 ,2021.

\bibitem{01石川正俊08}
石川正俊：情報科学技術の構造と情報教育,IDE 現代の高等教育,2021年8-9月号,No.633,pp.9-13,2021.

\bibitem{01石川正俊09}
Masahiro Hirano,Yuji Yamakawa,Taku Senoo,Norimasa Kishi,Masatoshi Ishikawa:Multiple Scale Aggregation with Patch Multiplexing for High-speed Inter-vehicle Distance Estimation,IEEE Intelligent Vehicles Symposium (IV),Proceedings,pp.1436-1443,2021.

\bibitem{01石川正俊10}
Hirofumi Sumi,Hironari Takehara,Jun Ohta,and Masatoshi Ishikawa:Advanced Multi-NIR Spectral Image Sensor with Optimized Vision Sensing System and Its Impact on Innovative Applications,2021 Symposium on VLSI Technology ,2021 Symposium on VLSI Technology Digest of Technical Papers,JFS4-8,pp.1-2,2021.

\bibitem{01石川正俊11}
Masahiko Yasui,Yoshihiro Watanabe,and Masatoshi Ishikawa：Dynamic and Occlusion-Robust Light Field Illumination,ACM SIGGRAPH ASIA 2021 Posters (SIGGRAPH ASIA 2021),Proceedings,Article No.35,pp.1–2,2021.

\bibitem{02早川智彦05}
Yuki Kubota,Tomohiko Hayakawa,Osamu Fukayama,and Masatoshi Ishikawa：Sequential estimation of psychophysical parameters based on the paired comparisons,2022 IEEE/SICE International Symposium on System Integration (SII 2022),pp.150-154,2022.

\bibitem{02早川智彦06}
Ke Yushan,Yushi Moko,Yuka Hiruma,Tomohiko Hayakawa,and Masatoshi Ishikawa：Silk printed retroreflective markers for infrastructure maintenance vehicles in tunnels,SPIE Smart Structures + NDE On Demand,2022 (accepted).

\bibitem{03黄守仁02}
Mamoru Oka,Kenichi Murakami,Shouren Huang,Hirofumi Sumi,Masatoshi Ishikawa and Yuji Yamakawa：High-speed Manipulation of Continuous Spreading and Aligning a Suspended Towel-like Object,2022 IEEE/SICE International Symposium on System Integration,2022.

\bibitem{04末石智大06}
Tomohiro Sueishi and Masatoshi Ishikawa:  Ellipses Ring Marker for High-speed Finger Tracking,The 27th ACM Symposium on Virtual Reality Software and Technology (VRST2021) (Osaka),Proceedings,Article No. 31,pp.1-5,2021.


\bibitem{04末石智大07}
Soichiro Matsumura,Tomohiro Sueishi,Shoji Yachida,and Masatoshi Ishikawa:Eye Vibration Detection Using High-speed Optical Tracking and Pupil Center Corneal Reflection,The 43rd Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC2021) (Virtual)/Proceedings,ThDT3.5,2021.

\bibitem{04末石智大08}
Ayumi Matsumoto,Tomohiro Sueishi,and Masatoshi Ishikawa：High-speed Gaze-oriented Projection by Cross-ratio-based Eye Tracking with Dual Infrared Imaging,2022 IEEE Conference on Virtual Reality and 3D User Interfaces Abstracts and Workshops (VRW2022),Proceedings,pp.594-595,2022.

\bibitem{04末石智大09}
Tomohiro Sueishi,Soichiro Matsumura,Shoji Yachida,and Masatoshi Ishikawa： Optical and Control Design of Bright-pupil Microsaccadic Artificial Eye,2022 IEEE/SICE International Symposium on System Integration (SII2022) Online,Proceedings,pp.760-765,2022.

\bibitem{05宮下令央04}
Leo Miyashita,Kentaro Fukamizu,and Masatoshi Ishikawa:Simultaneous Augmentation of Textures and Deformation Based on Dynamic Projection Mapping,SIGGRAPH Asia 2021,Real Time Live!,2021.

\bibitem{05宮下令央05}
Leo Miyashita,Kentaro Fukamizu,and Masatoshi Ishikawa: Simultaneous Augmentation of Textures and Deformation Based on Dynamic Projection Mapping,SIGGRAPH Asia 2021,Emerging Technologies,2021.

\bibitem{05宮下令央06}
Leo Miyashita,Yohta Kimura,Satoshi Tabata,and Masatoshi Ishikawa:High-speed simultaneous measurement of depth and normal for real-time 3D reconstruction,SPIE Optical Engineering + Applications,2021.

\bibitem{06田畑智志02}
Yuping Wang,Senwei Xie,Lihui Wang,Hongjin Xu,Satoshi Tabata,and Masatoshi Ishikawa：ARSlice: Head-Mounted Display Augmented with Dynamic Tracking and Projection,The 10th international conference on Computational Visual Media (CVM 2022),2022(accepted).

\bibitem{09李ソ賢01}
Seohyun Lee,Hyuno Kim,Hideo Higuchi,and Masatoshi Ishikawa:Classification of Metastatic Breast Cancer Cell Using Deep Learning Approach,2021 International conference on artificial intelligence in information and communication (ICAIIC),Proceedings,pp.425-428,2021.

\bibitem{kobayashi2-1}
Keijiro Nakagawa, Daisuk\'e Shimotoku, Junya Kawase and Hill Hiroki Kobayashi, "Sustainable Wildlife DTN: Wearable Animal Resource Optimization through Intergenerational Multi-hop Network Simulation.", Proceedings of 2021 17th International Conference on Wireless and Mobile Computing, Networking and Communications (IEEE WiMob), 2021.
\bibitem{kobayashi2-2}
Daisuk\'e Shimotoku, Junya Kawase, Herv\'e Glotin and Hill Hiroki Kobayashi, "Comparison Between Manual and Automated Annotations of Eco-Acoustic Recordings Collected in Fukushima Restricted Zone.", Proceedings of 2021 International Conference on Human-Computer Interaction (HCII 2021), 2021.  
\bibitem{ykuga33191433}
Yukito Ueno, Ryo Nakamura, Yohei Kuga, Hiroshi Esaki, P2PNIC: High-Speed Packet Forwarding by Direct Communication between NICs, IEEE INFOCOM 2021 - IEEE Conference on Computer Communications Workshops (INFOCOM WKSHPS), pp1-6, May, 2021.

\bibitem{ykuga32183289}
Hajime Tazaki, Akira Moroo, Yohei Kuga, Ryo Nakamura, How to design a library OS for practical containers?, Proceedings of the 17th ACM SIGPLAN/SIGOPS International Conference on Virtual Execution Environments, 16 Apr, 2021.

\bibitem{JIANG2-1}
Zhaonan Wang, Renhe Jiang, Hao Xue, Flora Salim, Xuan Song, Ryosuke Shibasaki, "Event-Aware Multimodal Mobility Nowcasting", Proceedings of Thirty-Sixth AAAI Conference on Artificial Intelligence (AAAI), 2022.
\bibitem{JIANG2-2}
Zhaonan Wang, Renhe Jiang, Zekun Cai, Zipei Fan, Xin Liu, Kyoung-Sook Kim, Xuan Song, Ryosuke Shibasaki, "Spatio-Temporal-Categorical Graph Neural Networks for Fine-Grained Multi-Incident Co-Prediction", Proceedings of 30th ACM International Conference on Information and Knowledge Management (CIKM), 2021.
\bibitem{JIANG2-3}
Renhe Jiang, Du Yin, Zhaonan Wang, Yizhuo Wang, Jinliang Deng, Hangchen Liu, Zekun Cai, Jinliang Deng, Xuan Song, Ryosuke Shibasaki, "DL-Traff: Survey and Benchmark of Deep Learning Models for Urban Traffic Prediction", Proceedings of 30th ACM International Conference on Information and Knowledge Management (CIKM), 2021.
\bibitem{JIANG2-4}
Renhe Jiang, Zhaonan Wang, Zekun Cai, Chuang Yang, Zipei Fan, Tianqi Xia, Go Matsubara, Hiroto Mizuseki, Xuan Song, Ryosuke Shibasaki, "Countrywide OD Matrix Prediction for COVID-19", Proceedings of the European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases (ECML PKDD), 2021. 
\bibitem{JIANG2-5}
Jinliang Deng, Xiusi Chen, Renhe Jiang, Xuan Song, Ivor W. Tsang, "ST-Norm Spatial and Temporal Normalization for Multi-variate Time Series Forecasting", Proceedings of 27th ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD), 2021.
\bibitem{JIANG2-6}
Zhaonan Wang, Tianqi Xia, Renhe Jiang, Xin Liu, Kyoung-Sook Kim, Xuan Song, Ryosuke Shibasaki, "Forecasting Ambulance Demand with Profiled Human Mobility via Heterogeneous Multi-graph Convolution Network”, Proceedings of the 37th IEEE International Conference on Data Engineering (ICDE), 2021. 
\bibitem{HNakamura2}
Satoshi Okada, Daisuke Miyamoto, Yuji Sekiya, Hiroshi Nakamura, ``New
LDoS Attack in Zigbee Network and its Possible Countermeasures'', The
5th IEEE International Workshop on Big Data and IoT Security in Smart
Computing, 6pages, Aug.  2021

\bibitem{HNakamura3}
Shaswot Shresthamali, Masaaki Kondo, Hiroshi Nakamura, ``Multi-objective
Reinforcement Learning for Energy Harvesting Wireless Sensor Nodes'',
14th IEEE International Symposium on Embedded Multicore Many-core
Systems-on-Chip (MCSoC 2021), 8pages, Dec. 2021

\bibitem{HNakamura4}
Satoshi Okada, Daisuke Miyamoto, Yuji Sekiya, Hideki Takase, Hiroshi
Nakamura, ``LDoS Attacker Detection Algorithms in Zigbee Network'',
Proceedings of the 14th IEEE International Conference on Internet of
Things, Dec. 2021

\bibitem{HNakamura5}
Siyi Hu, Masaaki Kondo, Yuan He, Ryuichi Sakamoto, Hao Zhang, Jun Zhou
and Hiroshi Nakamura, ``GraphDEAR: An Accelerator Architecture for
Exploiting Cache Locality in Graph Analytics Applications'', Proc. of 30
Euromicro International Conference on Parallel, Distributed, and
Network-based Processing, Mar. 2022


\bibitem{suzumura-sc2021}
Venkatesan T. Chakaravarthy, Shivmaran S. Pandian, Saurabh Raje, Yogish Sabharwal, Toyotaro Suzumura, Shashanka Ubaru, 
"Efficient scaling of dynamic graph neural networks". SC2021(The International Conference for High Performance Computing, Networking, Storage, and Analysis)

\bibitem{suzumura-smds21}
Shilei Zhang, Toyotaro Suzumura, Li Zhang, "DynGraphTrans: Dynamic Graph Embedding via Modified Universal Transformer Networks for Financial Transaction Data", IEEE SMDS 2021 (International Conference on Smart Data Services) 
\end{査読付}

%\begin{公開}{1}
%
%
%\end{公開}
%
%\begin{特許}{1}
%
%
%\end{特許}

\begin{発表}{1}

\bibitem{01石川正俊12}
谷内田尚司,並木重哲,小川拓也,細井利憲,石川正俊：高速カメラ物体認識技術を用いた錠剤外観検査装置,製剤機械技術学会誌,Vol.30,No.4,pp.35-40,2021.

\bibitem{02早川智彦07}
栃岡 陽麻里,早川 智彦,石川 正俊：身体感覚と視覚情報にずれが生じる低遅延没入環境におけるターゲットの加速度がユーザへ与える影響,第26回日本バーチャルリアリティ学会大会 (VRSJ2021),論文集,3B2-3,2021.

\bibitem{03黄守仁03}
村上 健一,黄 守仁,石川 正俊,山川 雄司：高速ビジュアルフィードバックを用いた高速３次元位置補償システムの開発,第22回計測自動制御学会システムインテグレーション部門講演会 (SI2021),講演会論文集,pp.1403-1405,2021.

\bibitem{03黄守仁04}
岡衛,村上健一,黄守仁,角博文,石川正俊,山川雄司:面状柔軟物の展開に向けたコーナーの状態認識と把持動作計画,第39回日本ロボット学会学術講演会（RSJ2021),講演会論文集,3F1-01,2021.

\bibitem{03黄守仁05}
上野永遠,黄守仁,石川正俊:上腕の一自由度回転運動に向けた高周波電気刺激フィードバック制御システムの構築,第39回日本ロボット学会学術講演会（RSJ2021),講演会論文集,RSJ2021AC2J1-01,2021

\bibitem{03黄守仁06}
長谷川雄大,黄守仁,山川雄司,石川正俊:閉リンク機構を用いた動的補償モジュールの開発,第39回日本ロボット学会学術講演会（RSJ2021),講演会論文集,RSJ2021AC2D2-05,2021.

\bibitem{04末石智大10}
末石智大,石川正俊：手指高速トラッキングに向けた楕円群指輪マーカーの開発,第22回計測自動制御学会システムインテグレーション部門講演会(SI2021),講演会論文集,pp.1382-1387,2021.

\bibitem{04末石智大11}
末石智大,松村蒼一郎,谷内田尚司,石川正俊:マイクロサッカード高精度計測に向けた動的な明瞳孔眼球模型の開発,第22回計測自動制御学会システムインテグレーション部門講演会(SI2021),講演会論文集,pp.2011-2016,2021.

\bibitem{04末石智大12}
松村蒼一郎,末石智大,井上満晶,谷内田尚司,石川正俊：光学系制御撮影下の角膜反射法によるマイクロサッカード検出高精度化の検討,第22回計測自動制御学会システムインテグレーション部門講演会(SI2021),講演会論文集,pp.2025-2028,2021.

\bibitem{04末石智大13}
三河祐梨,末石智大,石川正俊：球体姿勢に対応した回転相殺テクスチャの高速投影の残像効果による一軸回転可視化法の提案,第26回日本バーチャルリアリティ学会大会(VRSJ2021),論文集,2D2-5,2021.

\bibitem{04末石智大14}
三河祐梨,末石智大,渡辺義浩,石川正俊：VarioLight2円周マーカを用いた球体への広域かつ遮蔽に頑健なダイナミックプロジェクションマッピング,第27回画像センシングシンポジウム(SSII2021),講演論文集 IS1-25,2021.

\bibitem{ykuga36616798}
塙敏博, 中村遼, 空閑洋平, 杉木章義, 田浦健次朗, データ利活用に向けた仮想化プラットフォームmdxの基本性能評価, 研究報告ハイパフォーマンスコンピューティング（HPC）, 7, pp1-9, Mar, 2022.

\bibitem{ykuga36616852}
中村遼, 空閑洋平, AES67のソフトウェアによる実装の試行, 研究報告インターネットと運用技術（IOT）, 54, pp1-4, Feb, 2022.

\bibitem{HNakamura6}
仮屋 郷佑, 坂本 龍一, 中村 宏, ``動的スケジューリングによるマイクロサー
ビスの実行最適化'', 情報処理学会コンピュータシステム・シンポジウム論文
集, 2021,pages. 1-10 (2021-11-25)


\bibitem{suzumura-axies2021}
鈴村豊太郎, "データ活用社会創成プラットフォームmdxの設計・実装・運用〜多様な学際領域における共創に向けて～", 大学ICT推進協議会2021年度年次大会（AXIES2021), 2021年12月
\end{発表}

%\begin{特記}{1}
%
%
%\end{特記}

\begin{報道}{1}

\bibitem{01石川正俊13}
石川正俊：「ロボット」100年で次へ　東大特任教授・石川正俊氏に聞く　人のはるかに先を行く　機械性能極限まで発揮,電波新聞,令和3年7月8日.

\bibitem{01石川正俊14}
石川正俊：「高速反応や自律航行　ロボット研究進む　東大でオンライン公開講座」,電波新聞,令和3年6月17日.

\bibitem{01石川正俊15}
石川グループ研究室：MBS毎日,日曜日の初耳学,「VarioLight2,ダイナミックプロジェクションマッピング」,令和3年9月13日.

\bibitem{01石川正俊16}
石川グループ研究室：テレビ東京,日経ニュースプラス9,「ElaMorph projection,VarioLight2,高速トンネル検査」,令和3年6月8日.

\bibitem{01石川正俊17}
石川グループ研究室：TBS,あさチャン！,「ジャンケンロボット,高速道路トンネル検査」,令和3年6月28日.


\end{報道}
