\begin{雑誌論文}{1}
\bibitem{JIANG1901}
Zipei Fan, Xuan Song, Renhe Jiang, Quanjun Chen, and Ryosuke Shibasaki:
Decentralized Attention-based Personalized Human Mobility Prediction, Proceedings of the ACM on Interactive Mobile Wearable and Ubiquitous Technologies, Vol.3, No.4, pp1-26, December 2019.
\bibitem{JIANG2001}
Zipei Fan, Xuan Song, Quanjun Chen, Renhe Jiang, Ryosuke Shibasaki, and Kota Tsubouchi:  
Trajectory fingerprint: one-shot human trajectory identification using Siamese network, CCF Transactions on Pervasive Computing and Interaction, 2(2), 113-125, 2020.
\bibitem{JIANG2002}
Renhe Jiang, Quanjun Chen, Zekun Cai, Zipei Fan, Xuan Song, Kota Tsubouchi, and Ryosuke Shibasaki: 
Will You Go Where You Search? A Deep Learning Framework for Estimating User Search-and-Go Behavior, Neurocomputing, 2020.
\bibitem{JIANG2003}
Renhe Jiang, Xuan Song, Zipei Fan, Tianqi Xia, Zhaonan Wang, Quanjun Chen, Zekun Cai, and Ryosuke Shibasaki: 
Transfer Urban Human Mobility via POI Embedding over Multiple Cities, ACM/IMS Trans. Data Sci. 2, 1, Article 4, 26 pages, January 2021.
\end{雑誌論文}

\begin{査読付}{1}
\bibitem{JIANG1902}
Renhe Jiang, Xuan Song, Dou Huang, Xiaoya Song, Tianqi Xia, Zekun Cai, Zhaonan Wang, Kyoung-Sook Kim, and Ryosuke Shibasaki:
Deepurbanevent: A system for predicting citywide crowd dynamics at big events, Proceedings of The 25th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining (KDD'19), pp2114-2122, July 2019.
\bibitem{JIANG1903}
Zipei Fan, Quanjun Chen, Renhe Jiang, Ryosuke Shibasaki, Xuan Song, and Kota Tsubouchi:
Deep Multiple Instance Learning for Human Trajectory Identification, Proceedings of the 27th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems (SIGSPATIAL'19), pp512-515, November 2019.
\bibitem{JIANG1904}
Xiaodan Shi, Xiaowei Shao, Zipei Fan, Renhe Jiang, Haoran Zhang, Zhiling Guo, Guangming Wu, Wei Yuan, and Ryosuke Shibasaki:
Multimodal Interaction-Aware Trajectory Prediction in Crowded Space, Proceedings of The Thirty-Fourth AAAI Conference on Artificial Intelligence (AAAI'20), pp11982-11989, February 2020.
\bibitem{JIANG2004}
Satoshi Miyazawa, Xuan Song, Renhe Jiang, Zipei Fan, Ryosuke Shibasaki, and Taisei Sato:
City-Scale Human Mobility Prediction Model by Integrating Gnss Trajectories and Sns Data Using Long Short-Term Memory, ISPRS Annals of the Photogrammetry, Remote Sensing and Spatial Information Sciences, Volume V-4-2020, 2020, pp.87-94, August 2020.
\bibitem{JIANG2005}
Quanjun Chen, Renhe Jiang, Chuang Yang, Zekun Cai, Zipei Fan, Kota Tsubouchi, Xuan Song, Ryosuke Shibasaki: 
DualSIN: Dual Sequential Interaction Network for Human Intentional Mobility Prediction, Proceedings of the 28th International Conference on Advances in Geographic Information Systems (SIGSPATIAL '20), pp.283–292, November 2020.
\bibitem{JIANG2006}
Xiaodan Shi, Xiaowei Shao, Guangming Wu, Haoran Zhang, Zhiling Guo, Renhe Jiang, Ryosuke Shibasaki: 
Social-DPF: Socially acceptable distribution prediction of futures, Proceedings of The Thirty-Fifth AAAI Conference on Artificial Intelligence (AAAI'21), February 2021.
\end{査読付}


